Meta-analysis

### 2019-09-02 05_MetaAnalysis.Rmd
between trial variance calculated

@@

plot(BW_trial_variance ~ trial_mean, data = PM_MB_means_T)
abline(-0.01356,0.03076)
points(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole"),col = "red", pch = 3)
abline(-0.005162, 0.019892, col = "red")
points(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole"),col = "blue", pch = 3)
abline(-0.03962, 0.05454, col = "blue")

>>>>

All_Trials <- unique(PM_MB_means$Trial_ref)
PM_MB_means$TrialVariance <- NA

for(i in All_Trials){
   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"BW_trial_variance"]
}

PM_MB_means$TrialVariance

@@

plot(BW_trial_variance ~ trial_mean, data = PM_MB_means_T)
abline(-0.01356,0.03076)
